### 2023-05-10 docs/minutes/slides/document.tex
fprior_earth_corrected prior
he-8 for earth model

\date{EE/GW meeting, November 11, 2023}

@@

	\begin{itemize}
		\item \alert{Problem = overly narrow,biased posteriors}. Even for ``easy" systems!
	\end{itemize}

\includegraphics[width=0.5\textwidth,height=0.5\textwidth]{images/example_system}

$h = 10^{-2}, \sigma_m = 10^{-13}, \sigma_p = 0.0$

@@

		\begin{itemize}
		\item \alert{Problem} = overly narrow,biased posteriors
		\item Cause: noisy, likelihoods which are "locally Gaussian". Sampling gets stuck in a local optima and infers posteriors widths based on that optima. 
	\end{itemize}

@@

	\begin{enumerate}
		\item Don't be a Bayesian: Maximum likelihood / loss optimisation? 
		\item Be a Bayesian: Drop PSR terms from model?
		\item other...?
	\end{enumerate}

@@

\begin{frame}{Option 2: Drop PSR terms from model?}
	 \begin{equation}
		f_{\rm measured} = f_{\rm emitted} \, g(\tau; \bar{\theta})
		\label{eq:measureent}
	\end{equation}
	with
	\begin{align}
		g(\tau; \bar{\theta}) 
		& = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) - \cos(-\Omega \tau +\Phi_0 + \Omega (1 + \bar{n}\cdot \bar{q})  d) \right]
	\end{align}

@@

@@

	OK, but some biases...
\end{frame}

>>>>

\date{EE/GW meeting, May 11, 2023}

@@

	\begin{itemize}
		\item \alert{Problem = overly narrow,biased posteriors from nested sampling}. Even for ``easy" systems!
	\end{itemize}

Here is an easy system: $h = 10^{-2}, \sigma_m = 10^{-13}, \sigma_p = 0.0$ \newline 
\centering
\includegraphics[width=0.5\textwidth,height=0.5\textwidth]{images/example_system}

\raggedright
If the true declination $\delta = 1.0$, NS might give us a posterior of $\sim 0.95$ but variance v.v. small and posterior does not capture true value

@@

		\begin{itemize}
		\item \alert{Problem} = overly narrow,biased posteriors
		\item Cause: noisy, likelihoods which are "locally Gaussian". Sampling gets stuck in a local optima and infers posteriors widths based on that optima. 
%		\item Require $n_{live} > \frac{\rm prior \, volume}{\rm mode \,  footprint} = \frac{X}{\sigma^2}$
%		\begin{itemize}
%			\item For $\delta$ require $n_{live} > \frac{2 \pi}{10^{-5}} \sim 10^5 $
%			\item For $\omega$ require $n_{live} > \frac{10^4}{10^{-11}} \sim 10^7 $ 
%			\item Currently $n_{live} = 500$ parallelized on 32 cores $\sim 700$ minutes
%			\item Runtime scales $\mathcal{O}(n_{live}) \rightarrow 8000 $ hours for required $\delta$ sampling (just under 1 year!)
%
%		\end{itemize}
	\end{itemize}

@@

	\begin{enumerate}
		\item Better settings for sampler? E.g. more live points (how many?), massively parallel, optimized likelihood evaluations,...
		\item Maximum likelihood / loss optimisation? 
		\item Drop PSR terms from model?
		\item MCMC at higher temperatures (trades off evidence..., less efficient	)
		\item other...?
	\end{enumerate}

@@

\begin{frame}{Drop PSR terms from model?}
	 \begin{equation}
		f_{\rm measured} = f_{\rm emitted} \, g(\tau; \bar{\theta})
		\label{eq:measureent}
	\end{equation}
	with
	\begin{align}
		g(\tau; \bar{\theta}) 
		& = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) - \cos(-\Omega \tau +\Phi_0 + \Omega (1 + \bar{n}\cdot \bar{q})  d) \right]
	\end{align}

@@

\begin{frame}{Drop PSR terms from model?}

@@

	OK, but some biases. c.f. location of the maxima on the previous slide
\end{frame}
